---
title: "HW 03 - Great Lakes Fish Datasets"
author: "chris serrano"
date: "3/2/23"
output: html_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
```

```{r load-data, message = FALSE}
catch_data <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-06-08/fishing.csv')

fish_stock <- read_csv("data/great-lakes-fish-stock.csv")
```

## Exercises

### Exercise 1

```{r catch-data-subset}
catch_data <- select(catch_data, year, lake, species, region, values)
catch_data
```

```{r fish-stock-subset}
fish_stock <- select(fish_stock, YEAR, MONTH, LAKE, STATE_PROV, SPECIES, WEIGHT)
fish_stock
```

### Exercise 2

```{r glimpse-catch-data}
glimpse(catch_data)

```

```{r fish_stock}
glimpse(fish_stock)

```


### Exercise 3

```{r filter-catch, eval = FALSE}
catch_data <- catch_data %>% 
  filter(region == "U.S. Total",
         species == "CHS",
         lake == "MI")
```

```{r filter-stock, eval = FALSE}
fish_stock <- fish_stock %>% 
  filter(STATE_PROV %in% c("MI", "WI", "IL", "IN"),
         SPECIES == "CHS",
         LAKE == "MI")
```
### Exercise 4

CATCH DATA-
There are `r nrow(catch_data)` in the dataset.
First year is `r min(catch_data$year)` in the dataset.
Last year is `r max(catch_data$year)` in the dataset.

FISH STOCK-
There are `r nrow(fish_stock)` in the dataset.
First year is `r min(fish_stock$YEAR)` in the dataset.
Last year is `r max(fish_stock$YEAR)` in the dataset.


### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Code chunks provided

Remember to change eval = FALSE, to eval = TRUE, when you are ready to run the code/knit the document.

```{r finalize-fish-stock, eval = FALSE}
fish_stock_yearly <- fish_stock_yearly %>% 
  rename(year = YEAR) %>% 
  mutate(stock_weight_yr_lbs = as.integer(STOCK_WEIGHT_YR * 0.454 / 1000)) %>% # 1 lb = 1 kg * 0.454
  select(year, stock_weight_yr_lbs)
```

```{r finalize-catch-data, eval = FALSE}
catch_data <- catch_data %>% 
  rename(catch_weight_yr_lbs = values)
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.
