---
title: "Lab 03 - Great Lakes Fish Stocking"
author: "Insert your name here"
date: "Insert date here"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
fish_stock <- read_csv("data/great-lakes-fish-stock.csv")
```

## Exercises

### Exercise 1

```{r}
glimpse(fish_stock)
```


there are 8 variables and 56232 observations. each row represents an observation.

### Exercise 2

```{r fish_species}
salmon_stock <- fish_stock %>%
  filter(SPECIES %in% c("ATS", "CHS", "COS"), 
         !is.na(WEIGHT),
         LAKE != "ON")
```

```{r salmon_stock}
glimpse(salmon_stock)
```

In the data set there are 8 variables and 5131 observations. 
numerical variables= weight, agemonth, no stocked, species, year, and month.
string variables= lake and state.

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
