---
title: "Lab 03 - Great Lakes Fish Stocking"
author: "chris serrano"
date: "2/26/23"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
fish_stock <- read_csv("data/great-lakes-fish-stock.csv")
```

## Exercises

### Exercise 1 -.5

```{r}
glimpse(fish_stock)
```


there are 8 variables and 56232 observations. each row represents an observation.

### Exercise 2 -.5

```{r fish_species}
salmon_stock <- fish_stock %>%
  filter(SPECIES %in% c("ATS", "CHS", "COS"), 
         !is.na(WEIGHT),
         LAKE != "ON")
```

```{r salmon_stock}
glimpse(salmon_stock)
```

In the data set there are 8 variables and 5131 observations. 
numerical variables= weight, agemonth, no stocked, species, year, and month.
string variables= lake and state.

### Exercise 3


```{r salmon-weight}
salmon_stock <- salmon_stock %>%
  mutate(
    AVERAGE = WEIGHT / NO_STOCKED * 1000
  )
salmon_stock
```

The mutate() function merges variables together in this code WEIGHT and NO_STOCKED to create a new one in this code it was AVERAGE.

### Exercise 4

```{r summary-statistics}
salmon_stock %>% 
  group_by(LAKE) %>% 
  filter(YEAR > 1999) %>% 
  summarize(MEAN_NO_STOCKED = mean(NO_STOCKED, na.rm = TRUE),
MEAN_WEIGHT = mean(WEIGHT, na.rm = TRUE)) %>% 
  arrange(desc(MEAN_NO_STOCKED))
```

lake Huron and Superior have the largest salmon stocking event and lake Huron and Michigan have the largest mean weight.

### Exercise 5

```{r fish-species, weight, summary-statistics}
trout_stock <- fish_stock %>%
  filter(
    SPECIES %in% c("BKT", "BKN", "LAT", "RBT", "TRT"),
    !is.na(WEIGHT),
    LAKE != "ON"
  )

trout_stock <- trout_stock %>%
  mutate(
    AVERAGE = WEIGHT / NO_STOCKED * 1000)
    trout_stock
    

    trout_stock %>% 
  group_by(LAKE) %>% 
  summarize(MEAN_NO_STOCKED = mean(NO_STOCKED, na.rm = TRUE),
            MEAN_WEIGHT = mean(WEIGHT, na.rm = TRUE)) %>% 
  arrange(desc(MEAN_NO_STOCKED))
```

### Exercise 6

```{r annual-plot}
trout_and_salmon_stock <- fish_stock %>%
  filter(
    SPECIES %in% c("CHS", "BKT"),
    !is.na(WEIGHT)) %>%
    group_by(YEAR, SPECIES, LAKE) %>%
      summarise(ANNUAL_NO_STOCKED = sum(NO_STOCKED, na.rm = TRUE))
ggplot(trout_and_salmon_stock, aes(x = YEAR, y = ANNUAL_NO_STOCKED, color = SPECIES)) +
geom_line() +
  facet_wrap(~LAKE, ncol = 3) +
  theme_bw() +
  labs(
        x = "YEAR",
        y = "ANNUAL # OF CHINOOK SALMON AND BROWN TROUT STOCKED",
        color = "SPECIES"
      )
```
1. The species that was stocked at the highest rates was the Chinook salmon.
2. The lake that had the highest fishing stocking activities was Lake Michigan.
3. Stocking was at it's peak in Lake Michigan in 1988.


